---
title: "Making interactive aplication analytic with R"
subtitle: "Etika Dwi Lestari"
author: "elestari@wcs.org"
date: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
runtime: shiny
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

library(knitr)
opts_chunk$set(message = FALSE, warning = FALSE, cache = TRUE,
               fig.height = 6, fig.width = 8, fig.align = "center", 
               out.width = '100%') #out.height = '400px')
```

```{css, echo=FALSE}
.remark-slide-content {
  padding-top: 0px;
}


.remark-code {
  font-size: 13px;
}

.code10 .remark-code {
  font-size: 10%;
}

.code20 .remark-code {
  font-size: 20%;
}

.code30 .remark-code {
  font-size: 30%;
}

.code40 .remark-code {
  font-size: 40%;
}

.code50 .remark-code {
  font-size: 50%;
}

.code60 .remark-code {
  font-size: 60%;
}

.code70 .remark-code {
  font-size: 70%;
}

.code80 .remark-code {
  font-size: 80%;
}

.code90 .remark-code {
  font-size: 90%;
}
```

---
class: inverse, center, middle

# Mapping point data

---

## Palm trees in Sevilla

```{r echo=FALSE}

library(dplyr)
library(knitr)

data("quakes")

# Ambil 200 data sebagai contoh
quakes_sample <- quakes %>%
  sample_n(200)

kable(
  head(quakes_sample[, c("lat", "long", "mag", "depth")]),
  format = "html"
)

```



---

## Make interactive map (leaflet)

```{r}
library("leaflet")
```

https://rstudio.github.io/leaflet

([Cheatsheet](https://github.com/rstudio/cheatsheets/blob/main/leaflet.pdf))

---
## 🔹 Slide — Make interactive map (leaflet)

Lanjutkan dengan **leaflet map berbasis quakes**:

```{r cache=FALSE}
library(shiny)
library(bslib)

ui <- page_sidebar(
  title = "Hello Shiny!",
  sidebar = sidebar(
    sliderInput(
      inputId = "bins",
      label = "Number of bins:",
      min = 1,
      max = 50,
      value = 30
    )
  ),
  plotOutput(outputId = "distPlot")
)

server <- function(input, output) {

  output$distPlot <- renderPlot({

    x    <- faithful$waiting
    bins <- seq(min(x), max(x), length.out = input$bins + 1)

    hist(
      x,
      breaks = bins,
      col = "#007bc2",
      border = "white",
      xlab = "Waiting time (min)",
      main = "Histogram of waiting times"
    )
  })
}

shinyApp(ui = ui, server = server)
